---
title: "Lab6"
author: "Nicole Riordan"
date: "5/16/2021"
output: html_document
---

```{r setup, ```{r setup, cache = F}
knitr::opts_chunk$set(error = TRUE)
```

github repository

https://github.com/Adventures-R/twelvedays.git


```{r}
library(twelvedays)
```

```{r}
xmas2 <- read.csv("https://www.dropbox.com/s/ap2hqssese1ki4j/xmas_2.csv?dl=1")
pluralize_gift <- function(gift){
gift <- gift %>%
paste0("s")
new <- gift
str_replace(gift ,"ys$", "ies")
str_replace(gift ,"ooses", "eese")
return(new)
}
pluralize_gift (xmas2$Gift.Item)
xmas2 <- xmas2 %>%
  mutate(Gift.Item = as.vector(Gift.Item))%>%
  mutate(Gift.Item = paste0(xmas2$Gift.Item, "s"))%>%
  mutate(Gift.Item = str_replace_all(Gift.Item, "ys$", "ies"))%>%
  mutate(Gift.Item = str_replace_all(Gift.Item, "ooses", "eese"))
make_phrase <- function(num_word, item, verb, adjective, location){
  verb <- str_replace_na(verb, "")
  location <- str_replace_na(location, "")
  adjective <- str_replace_na(adjective, "")
 phrase <- str_c (num_word, adjective, item, verb, location, sep = " ")
return (phrase)
}
make_phrase( num_word = "ten", item = "lords", verb = "a-leaping", adjective = "", location = "")

xmas2 <- xmas2 %>%
  mutate(
    Full.Phrase = make_phrase(Day, Gift.Item, Verb, Adjective, Location)
  )
sing_day2 <- function(dataset, dayword, day, fullphrase)
  for (i in seq_along(list(fullphrase))) {
cat("On the", dayword, "day of Christmas\n")
 cat("My true love gave to me:\n")
cat(paste(fullphrase[i:1], collapse = "\n"), "\n\n")
}
pmap(xmas2, ~sing_day2(xmas,..2, ..1, ..7))

```

